Examining readability of text generated through GPT-3

### 2023-03-28 paper/paper.tex
move classifier logic and add evaluation
play around

@@

>>>>

\input{figs/lldl_means.tex}

LLDL (length of longest dependency link) is another metric that performs well in terms of level differentiation. It also reflects the common belief that the biggest difficulty spike in language learning - as shown by Figure~\ref{fig:lldl-mean}. As with most metrics, however, the natural progression of the CEFR levels is lost, particularly in the middle portions.

@@

This work attempted to gauge true readability levels of GPT-3 output texts with prompts across 10 topics and CEFR proficiency levels, optimising thus for the second language learning application environment. Outputs computed from the metrics set suggest that GPT-3 is at least somewhat aware of syntax and lexis when performin generation for a target readability level.

Future research into this topic could explore a wider variety of textual metrics, as this work only selected a handful that lent themselves particularly well to interpretation and did not require steep hardware requirements to obtain.
